---
title: "Case_Study_Group_32"
author: "Johannes Pascal Falkhofen, Johannes Fortmann, Felix Remien, Georg Viktor von Usedom, Lennart Rathje"
date: "2023-02-17"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1 Task

## 2 Library 

```{r, message=FALSE, warning = FALSE}
# Installation and loading of the "install.load" package if necessary 
# Note: The "install.load" package includes the install_load function
if(!require(install.load)){
  install.packages("install.load")
  library(install.load)
}

# Installation and loading of the stated packages if necessary   
install_load("dplyr", "readr", "data.table",  "shiny", "tidyr")
```

## 3 Data Import 

**Location of OEM1-plants**

*Imported variables: ORT, Werk, Breitengrad, L„ngengrad*

```{r, message=FALSE, warning = FALSE}
# OEM1 Plants: 11, 12
# (OME2 Plants: 21, 22)
# Plant 13 --> Not relevant consultation hours 

# Note: encoding was changed to "Latin-1" due to the "ä" contained in "Längengrad"
oem_locations <- fread("Data/Geodaten/OEM_Werke_2017-07-04_TrR.csv", data.table = FALSE, encoding = "Latin-1", drop = "PLZ")
oem_locations
```

**Vehicles produced by OEM1**

*Imported variables: ID_Fahrzeug, Produktionsdatum, Werksnummer, Fehlerhaft, Fehlerhaft_Datum*

```{r, message=FALSE, warning = FALSE}
# OEM1 produces only the vehicles of type 11 and 12  

# Vehicles type 11
vehicle_type11 <- fread("Data/Fahrzeug/Fahrzeuge_OEM1_Typ11.csv", header = TRUE, data.table = FALSE, select =  c("ID_Fahrzeug", "Produktionsdatum", "Werksnummer", "Fehlerhaft", "Fehlerhaft_Datum")) %>% 
  mutate(plant = as.factor(Werksnummer))
plants <- levels(vehicle_type11$plant)

# Vehicles type 12
vehicle_type12 <- fread("Data/Fahrzeug/Fahrzeuge_OEM1_Typ12.csv", header = TRUE, data.table = FALSE, select =  c("ID_Fahrzeug", "Produktionsdatum", "Werksnummer", "Fehlerhaft", "Fehlerhaft_Datum")) %>% 
  mutate(plant = as.factor(Werksnummer)) 
plants <- append(levels(vehicle_type12$plant), plants)
plants <- sort(unique(plants))

# Plants of OEM1 
plants
```

**Built-in components**

*Imported variables: All*

```{r, message=FALSE, warning = FALSE}
# Components within type 11
components_in_vehicle_type11 <- fread("Data/Fahrzeug/Bestandteile_Fahrzeuge_OEM1_Typ11.csv", header = TRUE, data.table = FALSE)

# Adding columns for the types of components built in 
# Body_component_type
components_in_vehicle_type11 <- components_in_vehicle_type11 %>% mutate(Body_component_type = substring(components_in_vehicle_type11$ID_Karosserie, 0, regexpr("-", components_in_vehicle_type11$ID_Karosserie) -1), .after = ID_Karosserie)
# Gearshift_component_type 
components_in_vehicle_type11 <- components_in_vehicle_type11 %>% mutate(Gearshift_component_type = substring(components_in_vehicle_type11$ID_Schaltung, 0, regexpr("-", components_in_vehicle_type11$ID_Schaltung) -1), .after = ID_Schaltung)
# Seats_component_type 
components_in_vehicle_type11 <- components_in_vehicle_type11 %>% mutate(Seats_component_type = substring(components_in_vehicle_type11$ID_Sitze, 0, regexpr("-", components_in_vehicle_type11$ID_Sitze) -1), .after = ID_Sitze)
# Engine_component_type
components_in_vehicle_type11 <- components_in_vehicle_type11 %>% mutate(Engine_component_type = substring(components_in_vehicle_type11$ID_Motor, 0, regexpr("-", components_in_vehicle_type11$ID_Motor) -1), .after = ID_Motor)

# Changing datatype of X_component_type to factor
components_in_vehicle_type11$Body_component_type <- as.factor(components_in_vehicle_type11$Body_component_type)
components_in_vehicle_type11$Gearshift_component_type <- as.factor(components_in_vehicle_type11$Gearshift_component_type)
components_in_vehicle_type11$Seats_component_type <- as.factor(components_in_vehicle_type11$Seats_component_type)
components_in_vehicle_type11$Engine_component_type <- as.factor(components_in_vehicle_type11$Engine_component_type)

# Identifying all components built in vehicle type 11 
components_vehicle_type11 <- c(levels(components_in_vehicle_type11$Body_component_type), levels(components_in_vehicle_type11$Gearshift_component_type), levels(components_in_vehicle_type11$Seats_component_type), levels(components_in_vehicle_type11$Engine_component_type))
# --> Component types built in: K4, K3AG1, K3SG1, K2LE1, K2ST1, K1BE1, K1DI1

# Remove X_component_type columns 
components_in_vehicle_type11 <- components_in_vehicle_type11 %>% select (-c(Body_component_type, Gearshift_component_type, Seats_component_type, Engine_component_type))

# Components within type 12
components_in_vehicle_type12 <- fread("Data/Fahrzeug/Bestandteile_Fahrzeuge_OEM1_Typ12.csv", header = TRUE, data.table = FALSE)

# Adding columns for the types of components built in 
# Body_component_type
components_in_vehicle_type12 <- components_in_vehicle_type12 %>% mutate(Body_component_type = substring(components_in_vehicle_type12$ID_Karosserie, 0, regexpr("-", components_in_vehicle_type12$ID_Karosserie) -1), .after = ID_Karosserie)
# Gearshift_component_type 
components_in_vehicle_type12 <- components_in_vehicle_type12 %>% mutate(Gearshift_component_type = substring(components_in_vehicle_type12$ID_Schaltung, 0, regexpr("-", components_in_vehicle_type12$ID_Schaltung) -1), .after = ID_Schaltung)
# Seats_component_type 
components_in_vehicle_type12 <- components_in_vehicle_type12 %>% mutate(Seats_component_type = substring(components_in_vehicle_type12$ID_Sitze, 0, regexpr("-", components_in_vehicle_type12$ID_Sitze) -1), .after = ID_Sitze)
# Engine_component_type
components_in_vehicle_type12 <- components_in_vehicle_type12 %>% mutate(Engine_component_type = substring(components_in_vehicle_type12$ID_Motor, 0, regexpr("-", components_in_vehicle_type12$ID_Motor) -1), .after = ID_Motor)

# Changing datatype of X_component_type to factor
components_in_vehicle_type12$Body_component_type <- as.factor(components_in_vehicle_type12$Body_component_type)
components_in_vehicle_type12$Gearshift_component_type <- as.factor(components_in_vehicle_type12$Gearshift_component_type)
components_in_vehicle_type12$Seats_component_type <- as.factor(components_in_vehicle_type12$Seats_component_type)
components_in_vehicle_type12$Engine_component_type <- as.factor(components_in_vehicle_type12$Engine_component_type)

# Identifying all components built in vehicle type 12
components_vehicle_type12 <- c(levels(components_in_vehicle_type12$Body_component_type), levels(components_in_vehicle_type12$Gearshift_component_type), levels(components_in_vehicle_type12$Seats_component_type), levels(components_in_vehicle_type12$Engine_component_type))
# --> Component types built in: K5, K3AG1, K3SG1, K2LE1, K2ST1, K1BE1, K1DI1

# Remove X_component_type columns 
components_in_vehicle_type12 <- components_in_vehicle_type12 %>% select (-c(Body_component_type, Gearshift_component_type, Seats_component_type, Engine_component_type))

# Components contained in vehicle type 11 and type 12 
components <- c(components_vehicle_type11, components_vehicle_type12)
components <- unique(components)
# --> Component types required: K4, K3AG1, K3SG1, K2LE1, K2ST1, K1BE1, K1DI1, K5    
components
```

**Individual components **

*Imported variables: id_X, component_failure, failure_date*

```{r, message=FALSE, warning = FALSE}
# Data import of required components  
# K4 --> Body
component_K4 <- fread("Data/Komponente/Komponente_K4.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft.x == 1 | Fehlerhaft.y == 1) %>% 
  mutate(component_failure = 1) %>% 
  mutate(id_body = if_else(is.na(ID_Karosserie.x), ID_Karosserie.y, ID_Karosserie.x)) %>% 
  mutate(failure_date = if_else(is.na(Fehlerhaft_Datum.x), Fehlerhaft_Datum.y, Fehlerhaft_Datum.x)) %>% 
  relocate(id_body, component_failure, failure_date) %>% 
  select(-(4:19)) 

# K3AG1 --> Gearshift
component_K3AG1 <- fread("Data/Komponente/Komponente_K3AG1.csv", header = TRUE, data.table = FALSE) %>% filter(Fehlerhaft.x == 1 | Fehlerhaft.y == 1 | Fehlerhaft == 1) %>% mutate(component_failure = 1) %>% 
  mutate(id_gearshift = 
     if_else(!is.na(ID_Schaltung.x), ID_Schaltung.x, 
     if_else(!is.na(ID_Schaltung.y), ID_Schaltung.y, 
     if_else(!is.na(ID_Schaltung), ID_Schaltung, NA)))) %>% 
  mutate(failure_date = 
     if_else(!is.na(Fehlerhaft_Datum.x), Fehlerhaft_Datum.x, 
     if_else(!is.na(Fehlerhaft_Datum.y), Fehlerhaft_Datum.y, 
     if_else(!is.na(Fehlerhaft_Datum), Fehlerhaft_Datum, NA)))) %>% relocate(id_gearshift, component_failure, failure_date) %>% 
  select(-(4:26)) 
   
# K3SG1 --> Gearshift  
component_K3SG1 <- fread("Data/Komponente/Komponente_K3SG1.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft.x == 1 | Fehlerhaft.y == 1) %>% 
  mutate(component_failure = 1) %>% 
  mutate(id_gearshift = if_else(!is.na(ID_Schaltung.x), ID_Schaltung.x, ID_Schaltung.y)) %>% 
  mutate(failure_date = if_else(!is.na(Fehlerhaft_Datum.x), Fehlerhaft_Datum.x, Fehlerhaft_Datum.y)) %>% 
  relocate(id_gearshift, component_failure, failure_date) %>% 
  select(-(4:19))   

# K2LE1 --> seats
txt <- readLines("Data/Komponente/Komponente_K2LE1.txt")
txt <- gsub("II",",",txt)
txt <- gsub("\v","\n",txt)
component_K2LE1 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
  filter(Fehlerhaft.x == 1 | Fehlerhaft.y == 1) %>% 
  mutate(component_failure = 1) %>% 
  mutate(id_seats = if_else(!is.na(ID_Sitze.x), ID_Sitze.x, ID_Sitze.y)) %>% 
  mutate(failure_date = if_else(!is.na(Fehlerhaft_Datum.x), Fehlerhaft_Datum.x, Fehlerhaft_Datum.y)) %>% 
  relocate(id_seats, component_failure, failure_date) %>%
  select(-(4:19))
rm(txt)

# K2ST1 --> seats
component_K2ST1 <- fread("Data/Komponente/Komponente_K2ST1.txt", data.table = FALSE) %>% 
  filter(Fehlerhaft == 1) %>% 
  rename(id_seats = ID_Sitze, component_failure = Fehlerhaft, failure_date = Fehlerhaft_Datum) %>% 
  relocate(id_seats, component_failure, failure_date) %>% 
  select(-(4:9))  

# K1BE1 --> engine
component_K1BE1 <- fread("Data/Komponente/Komponente_K1BE1.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft == 1) %>% 
  rename(id_engine = ID_Motor, component_failure = Fehlerhaft, failure_date = Fehlerhaft_Datum) %>% 
  relocate(id_engine, component_failure, failure_date) %>% 
  select(-(4:10))  

# K1DI1 --> engine  
component_K1DI1 <- fread("Data/Komponente/Komponente_K1DI1.csv", header = TRUE, data.table = FALSE) %>% filter(Fehlerhaft.x == 1 | Fehlerhaft.y == 1 | Fehlerhaft == 1) %>% mutate(component_failure = 1) %>% 
  mutate(id_engine = 
     if_else(!is.na(ID_Motor.x), ID_Motor.x, 
     if_else(!is.na(ID_Motor.y), ID_Motor.y, 
     if_else(!is.na(ID_Motor), ID_Motor, NA)))) %>% 
  mutate(failure_date = 
     if_else(!is.na(Fehlerhaft_Datum.x), Fehlerhaft_Datum.x, 
     if_else(!is.na(Fehlerhaft_Datum.y), Fehlerhaft_Datum.y, 
     if_else(!is.na(Fehlerhaft_Datum), Fehlerhaft_Datum, NA)))) %>% 
  relocate(id_engine, component_failure, failure_date) %>% 
  select(-(4:26)) 

# K5 --> body
component_K5 <- fread("Data/Komponente/Komponente_K5.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft.x == 1 | Fehlerhaft.y == 1) %>% 
  mutate(component_failure = 1) %>% 
  mutate(id_body = if_else(!is.na(ID_Karosserie.x), ID_Karosserie.x, ID_Karosserie.y)) %>% 
  mutate(failure_date = if_else(!is.na(Fehlerhaft_Datum.x), Fehlerhaft_Datum.x, Fehlerhaft_Datum.y)) %>% 
  relocate(id_body, component_failure, failure_date) %>%
  select(-(4:19)) 
```

Parts in components 

```{r, message=FALSE, warning = FALSE}
# K4
parts_in_component_K4 <- fread("Data/Komponente/Bestandteile_Komponente_K4.csv", header = TRUE, data.table = FALSE)

# K3AG1
parts_in_component_K3AG1 <- fread("Data/Komponente/Bestandteile_Komponente_K3AG1.csv", header = TRUE, data.table = FALSE)

# K3SG1
parts_in_component_K3SG1 <- fread("Data/Komponente/Bestandteile_Komponente_K3SG1.csv", header = TRUE, data.table = FALSE)

# K2LE1
parts_in_component_K2LE1 <- fread("Data/Komponente/Bestandteile_Komponente_K2LE1.csv", header = TRUE, data.table = FALSE)

# K2ST1
parts_in_component_K2ST1 <- fread("Data/Komponente/Bestandteile_Komponente_K2ST1.csv", header = TRUE, data.table = FALSE)

# K1BE1
parts_in_component_K1BE1 <- fread("Data/Komponente/Bestandteile_Komponente_K1BE1.csv", header = TRUE, data.table = FALSE)

# K1DI1
parts_in_component_K1DI1 <- fread("Data/Komponente/Bestandteile_Komponente_K1DI1.csv", header = TRUE, data.table = FALSE)

# K5
parts_in_component_K5 <- fread("Data/Komponente/Bestandteile_Komponente_K5.csv", header = TRUE, data.table = FALSE)

parts <- c()
parts <- append(parts, colnames(parts_in_component_K4))
parts <- append(parts, colnames(parts_in_component_K3AG1))
parts <- append(parts, colnames(parts_in_component_K3SG1))
parts <- append(parts, colnames(parts_in_component_K2LE1))
parts <- append(parts, colnames(parts_in_component_K2ST1))
parts <- append(parts, colnames(parts_in_component_K1BE1))
parts <- append(parts, colnames(parts_in_component_K1DI1))
parts <- append(parts, colnames(parts_in_component_K5))
```

Types of parts 

```{r, message=FALSE, warning = FALSE}
# Remove duplicates 
parts <- unique(parts)

# Remove entries which are not parts 
parts <- parts[! parts %in% c("X1", "V1", "X", "K4")]
parts <- gsub("ID_", "", parts)
parts <- setdiff(parts, components) 
sort(parts)
```

Individual parts 

**Individual parts **

*Imported variables: id_TX, part_failure, failure_date*

```{r, message=FALSE, warning = FALSE}
# T1
txt <- readLines("Data/Einzelteil/Einzelteil_T01.txt")
txt <- gsub(" | | ",",",txt, fixed = TRUE)
txt <- gsub(" ","\n",txt, fixed = TRUE)
part_T01 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
  filter(Fehlerhaft.x == 1 | Fehlerhaft.y == 1 | Fehlerhaft == 1) %>% mutate(part_failure = 1) %>% 
  mutate(id_T01 = 
     if_else(!is.na(ID_T01.x), ID_T01.x, 
     if_else(!is.na(ID_T01.y), ID_T01.y, 
     if_else(!is.na(ID_T01), ID_T01, NA)))) %>% 
  mutate(production_date = 
     if_else(!is.na(Produktionsdatum.x), Produktionsdatum.x, 
     if_else(!is.na(Produktionsdatum.y), Produktionsdatum.y, 
     if_else(!is.na(Produktionsdatum), Produktionsdatum, NA)))) %>% 
  mutate(failure_date = 
     if_else(!is.na(Fehlerhaft_Datum.x), Fehlerhaft_Datum.x, 
     if_else(!is.na(Fehlerhaft_Datum.y), Fehlerhaft_Datum.y, 
     if_else(!is.na(Fehlerhaft_Datum), Fehlerhaft_Datum, NA)))) %>% 
  relocate(id_T01, production_date, part_failure, failure_date) %>% 
  select(-(5:27)) 
rm(txt)

# T2
txt <- readLines("Data/Einzelteil/Einzelteil_T02.txt")
txt <- gsub("  ",",",txt, fixed = TRUE)
txt <- gsub("\t","\n",txt, fixed = TRUE)
part_T02 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
  filter(Fehlerhaft.x == 1 | Fehlerhaft.y == 1) %>% 
  mutate(part_failure = 1) %>% 
  mutate(id_T02 = if_else(!is.na(ID_T02.x), ID_T02.x, ID_T02.y)) %>% 
  mutate(production_date = if_else(!is.na(Produktionsdatum.x), Produktionsdatum.x, Produktionsdatum.y)) %>% 
  mutate(failure_date = if_else(!is.na(Fehlerhaft_Datum.x), Fehlerhaft_Datum.x, Fehlerhaft_Datum.y)) %>% 
  relocate(id_T02, production_date, part_failure, failure_date) %>% 
  select(-(5:20)) 
rm(txt)

# T3
txt <- readLines("Data/Einzelteil/Einzelteil_T03.txt")
txt <- gsub("|",",",txt, fixed = TRUE)
txt <- gsub("\v","\n",txt, fixed = TRUE)
part_T03 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
  filter(Fehlerhaft == 1) %>% 
  rename(id_T03 = ID_T03, production_date = Produktionsdatum_Origin_01011970, part_failure = Fehlerhaft, failure_date = Fehlerhaft_Datum) %>% 
  relocate(id_T03, production_date, part_failure, failure_date) %>% 
  mutate(production_date = as.IDate(production_date, origin = "1970-01-01")) %>% 
  select(-(5:10))  
rm(txt)

# T4
part_T04 <- fread("Data/Einzelteil/Einzelteil_T04.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft == 1) %>% 
  rename(id_T04 = ID_T04, production_date = Produktionsdatum_Origin_01011970, part_failure = Fehlerhaft, failure_date = Fehlerhaft_Datum) %>% 
  relocate(id_T04, production_date, part_failure, failure_date) %>% 
  mutate(production_date = as.IDate(production_date, origin = "1970-01-01")) %>% 
  select(-(5:10))  

# T5
part_T05 <- fread("Data/Einzelteil/Einzelteil_T05.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft.x == 1 | Fehlerhaft.y == 1) %>% 
  mutate(part_failure = 1) %>% 
  mutate(id_T05 = if_else(!is.na(ID_T05.x), ID_T05.x, ID_T05.y)) %>% 
  mutate(production_date = if_else(!is.na(Produktionsdatum.x), Produktionsdatum.x, Produktionsdatum.y)) %>% 
  mutate(failure_date = if_else(!is.na(Fehlerhaft_Datum.x), Fehlerhaft_Datum.x, Fehlerhaft_Datum.y)) %>% 
  relocate(id_T05, production_date, part_failure, failure_date) %>% 
  select(-(5:20)) 

# T6 
part_T06 <- fread("Data/Einzelteil/Einzelteil_T06.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft == 1) %>% 
  rename(id_T06 = ID_T06, production_date = Produktionsdatum_Origin_01011970, part_failure = Fehlerhaft, failure_date = Fehlerhaft_Datum) %>% 
  relocate(id_T06, production_date, part_failure, failure_date) %>% 
  mutate(production_date = as.IDate(production_date, origin = "1970-01-01")) %>% 
  select(-(5:10))   

# T11
txt <- readLines("Data/Einzelteil/Einzelteil_T11.txt")
txt <- gsub("\t",",",txt, fixed = TRUE)
txt <- gsub("\f","\n",txt, fixed = TRUE)
part_T11 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
  filter(Fehlerhaft == 1) %>% 
  rename(id_T11 = ID_T11, production_date = Produktionsdatum_Origin_01011970, part_failure = Fehlerhaft, failure_date = Fehlerhaft_Datum) %>% 
  relocate(id_T11, production_date, part_failure, failure_date) %>% 
  mutate(production_date = as.IDate(production_date, origin = "1970-01-01")) %>% 
  select(-(5:10))   
rm(txt)

# T12
part_T12 <- fread("Data/Einzelteil/Einzelteil_T12.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft.x == 1 | Fehlerhaft.y == 1 | Fehlerhaft == 1) %>% mutate(part_failure = 1) %>% 
  mutate(id_T12 = 
     if_else(!is.na(ID_T12.x), ID_T12.x, 
     if_else(!is.na(ID_T12.y), ID_T12.y, 
     if_else(!is.na(ID_T12), ID_T12, NA)))) %>% 
  mutate(production_date = 
     if_else(!is.na(Produktionsdatum.x), Produktionsdatum.x, 
     if_else(!is.na(Produktionsdatum.y), Produktionsdatum.y, 
     if_else(!is.na(Produktionsdatum), Produktionsdatum, NA)))) %>% 
  mutate(failure_date = 
     if_else(!is.na(Fehlerhaft_Datum.x), Fehlerhaft_Datum.x, 
     if_else(!is.na(Fehlerhaft_Datum.y), Fehlerhaft_Datum.y, 
     if_else(!is.na(Fehlerhaft_Datum), Fehlerhaft_Datum, NA)))) %>% 
  relocate(id_T12, production_date, part_failure, failure_date) %>% 
  select(-(5:27)) 

# T13
part_T13 <- fread("Data/Einzelteil/Einzelteil_T13.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft == 1) %>% 
  rename(id_T13 = ID_T13, production_date = Produktionsdatum_Origin_01011970, part_failure = Fehlerhaft, failure_date = Fehlerhaft_Datum) %>% 
  relocate(id_T13, production_date, part_failure, failure_date) %>% 
  mutate(production_date = as.IDate(production_date, origin = "1970-01-01")) %>% 
  select(-(5:10))   

# T14
part_T14 <- fread("Data/Einzelteil/Einzelteil_T14.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft == 1) %>% 
  rename(id_T14 = ID_T14, production_date = Produktionsdatum_Origin_01011970, part_failure = Fehlerhaft, failure_date = Fehlerhaft_Datum) %>% 
  relocate(id_T14, production_date, part_failure, failure_date) %>% 
  mutate(production_date = as.IDate(production_date, origin = "1970-01-01")) %>% 
  select(-(5:10))   

# T15
part_T15 <- fread("Data/Einzelteil/Einzelteil_T15.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft.x == 1 | Fehlerhaft.y == 1) %>% 
  mutate(part_failure = 1) %>% 
  mutate(id_T15 = if_else(!is.na(ID_T15.x), ID_T15.x, ID_T15.y)) %>% 
  mutate(production_date = if_else(!is.na(Produktionsdatum.x), Produktionsdatum.x, Produktionsdatum.y)) %>% 
  mutate(failure_date = if_else(!is.na(Fehlerhaft_Datum.x), Fehlerhaft_Datum.x, Fehlerhaft_Datum.y)) %>% 
  relocate(id_T15, production_date, part_failure, failure_date) %>% 
  select(-(5:20)) 

# T21
part_T21 <- fread("Data/Einzelteil/Einzelteil_T21.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft == 1) %>% 
  rename(id_T21 = ID_T21, production_date = Produktionsdatum_Origin_01011970, part_failure = Fehlerhaft, failure_date = Fehlerhaft_Datum) %>% 
  relocate(id_T21, production_date, part_failure, failure_date) %>% 
  mutate(production_date = as.IDate(production_date, origin = "1970-01-01")) %>% 
  select(-(5:10))   

# T22
txt <- readLines("Data/Einzelteil/Einzelteil_T22.txt")
txt <- gsub("\"\t\"",",",txt)
txt <- gsub("\"\t",",",txt)
txt <- gsub("\t\"",",",txt)
txt <- gsub("\t",",",txt)
txt <- gsub("\"\"","\n",txt)
txt <- gsub("\"","\n",txt)
part_T22 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
  filter(Fehlerhaft.x == 1 | Fehlerhaft.y == 1 | Fehlerhaft == 1) %>% mutate(part_failure = 1) %>% 
  mutate(id_T22 = 
     if_else(!is.na(ID_T22.x), ID_T22.x, 
     if_else(!is.na(ID_T22.y), ID_T22.y, 
     if_else(!is.na(ID_T22), ID_T22, NA)))) %>% 
  mutate(production_date = 
     if_else(!is.na(Produktionsdatum.x), Produktionsdatum.x, 
     if_else(!is.na(Produktionsdatum.y), Produktionsdatum.y, 
     if_else(!is.na(Produktionsdatum), Produktionsdatum, NA)))) %>% 
  mutate(failure_date = 
     if_else(!is.na(Fehlerhaft_Datum.x), Fehlerhaft_Datum.x, 
     if_else(!is.na(Fehlerhaft_Datum.y), Fehlerhaft_Datum.y, 
     if_else(!is.na(Fehlerhaft_Datum), Fehlerhaft_Datum, NA)))) %>% 
  relocate(id_T22, production_date, part_failure, failure_date) %>% 
  select(-(5:27)) 

# T23
part_T23 <- fread("Data/Einzelteil/Einzelteil_T23.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft.x == 1 | Fehlerhaft.y == 1) %>% 
  mutate(part_failure = 1) %>% 
  mutate(id_T23 = if_else(!is.na(ID_T23.x), ID_T23.x, ID_T23.y)) %>% 
  mutate(production_date = if_else(!is.na(Produktionsdatum.x), Produktionsdatum.x, Produktionsdatum.y)) %>% 
  mutate(failure_date = if_else(!is.na(Fehlerhaft_Datum.x), Fehlerhaft_Datum.x, Fehlerhaft_Datum.y)) %>% 
  relocate(id_T23, production_date, part_failure, failure_date) %>% 
  select(-(5:20)) 

# T24
txt <- readLines("Data/Einzelteil/Einzelteil_T24.txt")
txt <- gsub("  ",",",txt, fixed = TRUE)
txt <- gsub("\f","\n",txt, fixed = TRUE)
part_T24 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
  filter(Fehlerhaft.x == 1 | Fehlerhaft.y == 1 | Fehlerhaft == 1) %>% mutate(part_failure = 1) %>% 
  mutate(id_T24 = 
     if_else(!is.na(ID_T24.x), ID_T24.x, 
     if_else(!is.na(ID_T24.y), ID_T24.y, 
     if_else(!is.na(ID_T24), ID_T24, NA)))) %>% 
  mutate(production_date = 
     if_else(!is.na(Produktionsdatum.x), Produktionsdatum.x, 
     if_else(!is.na(Produktionsdatum.y), Produktionsdatum.y, 
     if_else(!is.na(Produktionsdatum), Produktionsdatum, NA)))) %>% 
  mutate(failure_date = 
     if_else(!is.na(Fehlerhaft_Datum.x), Fehlerhaft_Datum.x, 
     if_else(!is.na(Fehlerhaft_Datum.y), Fehlerhaft_Datum.y, 
     if_else(!is.na(Fehlerhaft_Datum), Fehlerhaft_Datum, NA)))) %>% 
  relocate(id_T24, production_date, part_failure, failure_date) %>% 
  select(-(5:27)) 
rm(txt)

# T25
part_T25 <- fread("Data/Einzelteil/Einzelteil_T25.csv", header = TRUE, data.table = FALSE, nrows = 50) %>% 
  filter(Fehlerhaft == 1) %>% 
  rename(id_T25 = ID_T25, production_date = Produktionsdatum_Origin_01011970, part_failure = Fehlerhaft, failure_date = Fehlerhaft_Datum) %>% 
  relocate(id_T25, production_date, part_failure, failure_date) %>% 
  mutate(production_date = as.IDate(production_date, origin = "1970-01-01")) %>% 
  select(-(5:10))   

# T30
part_T30 <- fread("Data/Einzelteil/Einzelteil_T30.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft.x == 1 | Fehlerhaft.y == 1 | Fehlerhaft == 1) %>% mutate(part_failure = 1) %>% 
  mutate(id_T30 = 
     if_else(!is.na(ID_T30.x), ID_T30.x, 
     if_else(!is.na(ID_T30.y), ID_T30.y, 
     if_else(!is.na(ID_T30), ID_T30, NA)))) %>% 
  mutate(production_date = 
     if_else(!is.na(Produktionsdatum.x), Produktionsdatum.x, 
     if_else(!is.na(Produktionsdatum.y), Produktionsdatum.y, 
     if_else(!is.na(Produktionsdatum), Produktionsdatum, NA)))) %>% 
  mutate(failure_date = 
     if_else(!is.na(Fehlerhaft_Datum.x), Fehlerhaft_Datum.x, 
     if_else(!is.na(Fehlerhaft_Datum.y), Fehlerhaft_Datum.y, 
     if_else(!is.na(Fehlerhaft_Datum), Fehlerhaft_Datum, NA)))) %>% 
  relocate(id_T30, production_date, part_failure, failure_date) %>% 
  select(-(5:27)) 

# T31
txt <- readLines("Data/Einzelteil/Einzelteil_T31.txt")
txt <- gsub("  ",",",txt, fixed = TRUE)
txt <- gsub("\b","\n",txt, fixed = TRUE)
part_T31 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
  filter(Fehlerhaft == 1) %>% 
  rename(id_T31 = ID_T31, production_date = Produktionsdatum_Origin_01011970, part_failure = Fehlerhaft, failure_date = Fehlerhaft_Datum) %>% 
  relocate(id_T31, production_date, part_failure, failure_date) %>% 
  mutate(production_date = as.IDate(production_date, origin = "1970-01-01")) %>% 
  select(-(5:10))   
rm(txt)

# T32
part_T32 <- fread("Data/Einzelteil/Einzelteil_T32.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft.x == 1 | Fehlerhaft.y == 1) %>% 
  mutate(part_failure = 1) %>% 
  mutate(id_T32 = if_else(!is.na(ID_T32.x), ID_T32.x, ID_T32.y)) %>% 
  mutate(production_date = if_else(!is.na(Produktionsdatum.x), Produktionsdatum.x, Produktionsdatum.y)) %>% 
  mutate(failure_date = if_else(!is.na(Fehlerhaft_Datum.x), Fehlerhaft_Datum.x, Fehlerhaft_Datum.y)) %>% 
  relocate(id_T32, production_date, part_failure, failure_date) %>% 
  select(-(5:20)) 

# T33
part_T33 <- fread("Data/Einzelteil/Einzelteil_T33.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft == 1) %>% 
  rename(id_T33 = ID_T33, production_date = Produktionsdatum_Origin_01011970, part_failure = Fehlerhaft, failure_date = Fehlerhaft_Datum) %>% 
  relocate(id_T33, production_date, part_failure, failure_date) %>% 
  mutate(production_date = as.IDate(production_date, origin = "1970-01-01")) %>% 
  select(-(5:10))   
```

## 4 Data Preparation

Often times imported raw data is in an untidy and unstructured format which is unsuitable for further data analysis. 

Generally data sets should fulfill the following three requirements in order to be in a *tidy* data format (slide 9)[1]: 

1. Each variable has its own column. 
2. Each observation has its own row. 
3. Each observation value has its own cell. 

Furthermore, attributes contributing to good data quality are without limitation (slide 7)[1]: 

* Incomplete data 
  + Do all required cells contain data? 
  + Are empty cells meaningful or flawed? 
* Inaccurate data 
  + Are all variables in a suitable data format?
* Inconsistent data 
  +
* Redundant data 
  + 

In chapter 4.1 the imported data is examined before it is cleaned in chapter 4.2. 

### 4.1 Data Investigation 

In order to get an broad overview of each data set the following functions are applied (slide 10)[1]: 

* *glimpse()*: Shows each variable, its data type as well as several observations 
* *summary()*: Provides an overview over the distribution of variables containing numbers 

**Location of OEM1-plants**

```{r, message=FALSE, warning = FALSE}
glimpse(oem_locations)
```

**Vehicles produced by OEM1**

```{r, message=FALSE, warning = FALSE}
glimpse(vehicle_type11)
```

```{r, message=FALSE, warning = FALSE}
glimpse(vehicle_type12)
```

### 4.2 Data Cleaning 

**Location of OEM1-plants**

```{r, message=FALSE, warning = FALSE}
oem_locations <- oem_locations %>%
  mutate(location = as.factor(ORT)) %>%
  mutate(plant = as.factor(substring(oem_locations$Werk, 2, 3))) %>%
  mutate(latitude = Breitengrad) %>%
  mutate(longitude = oem_locations[,4]) %>% 
  select(-(1:4))

glimpse(oem_locations)  
```

**Vehicles produced by OEM1**

```{r, message=FALSE, warning = FALSE}
vehicle_type11 <- vehicle_type11 %>%
  mutate(id_vehicle = as.factor(ID_Fahrzeug)) %>% 
  mutate(vehicle_production_date = Produktionsdatum) %>% 
  mutate(plant = as.factor(Werksnummer)) %>% 
  mutate(vehicle_failure = as.factor(Fehlerhaft)) %>%
  mutate(failure_date = Fehlerhaft_Datum) %>%
  relocate(id_vehicle, plant, vehicle_production_date, vehicle_failure, failure_date) %>%
  select(-(6:10))

glimpse(vehicle_type11)
```

```{r, message=FALSE, warning = FALSE}
vehicle_type12 <- vehicle_type12 %>%
  mutate(id_vehicle = as.factor(ID_Fahrzeug)) %>% 
  mutate(vehicle_production_date = Produktionsdatum) %>% 
  mutate(plant = as.factor(Werksnummer)) %>% 
  mutate(vehicle_failure = as.factor(Fehlerhaft)) %>%
  mutate(failure_date = Fehlerhaft_Datum) %>%
  relocate(id_vehicle, plant, vehicle_production_date, vehicle_failure, failure_date) %>%
  select(-(6:10))

glimpse(vehicle_type12)
```

## 5 Creation of the Final Dataset

```{r, message=FALSE, warning = FALSE}

```

## 6 Evaluation

## 7 Results

## 8 Sources

[1]	Fachgebiet Qualitätswissenschaft, “Skript: Tidy,” Berlin, Nov. 08, 2023. [Online]. Available: https://isis.tu-berlin.de/pluginfile.php/2444052/mod_resource/content/1/VL04_Tidy.pdf